The Impact of News Sentiment on MSFT

### 2024-01-21 Zedan_Wullschleger_MSFT_project/MSFT.Rmd
final commit

```{r echo=FALSE, include=TRUE}
# Casuality test for VADAR
causality(MSFT.vadar_VAR, cause="News_Sentiment")["Granger"] 
```
The p-value of 0.008237 from the Granger causality test suggests that reddit posts sentiment is indeed a causal driver of MSFT stock price. This result leads us to accept the hypothesis that changes in news sentiment have a predictive effect on Microsoft stock returns.

## Forecasting
We will use the VADAR VAR model for forecasting purposes to see if the inclusion of the reddit posts sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the reddit posts sentiment data of the testing period.

>>>>

```{r echo=FALSE, include=TRUE}
# Casuality test for VADER
causality(MSFT.vadar_VAR, cause="News_Sentiment")["Granger"] 
```
The p-value of 0.008237 from the Granger causality test suggests that reddit posts sentiment is indeed a causal driver of MSFT stock price. This result leads us to accept the hypothesis that changes in news sentiment have a predictive effect on Microsoft stock returns.

## Forecasting
We will use the VADER VAR model for forecasting purposes to see if the inclusion of the reddit posts sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the reddit posts sentiment data of the testing period.
